Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-04-19 docs/00-manuscripts/ieee/ieee-manuscript.tex
Disc: restructure and reformat sections, rename "derivation of indices" to a more general term

\subsection{Derivation of Indices}

\noindent The decision to use a buffer of 2 m to generate the index value for each observation has to be seen critical.
Due to the reported geometric offset of up to 1 m for the hyperspectral data, the possibility of assigning a wrong pixel value to a tree observation would be high.
Using a buffer of more than 2 meters increases the probability of including information from other trees into the pixel value, blurring the actual value of the tree observation.
In our view using a buffer of 2 m is a good compromise between including information of too many surrounding trees and not accounting for the geometric offset.
Even though we provide no results showing the influence of multiple buffer values on the extraction, we hypothesize that the relationships between features would not change substantially, leading to the almost identical model results.

@@

\subsubsection{Algorithm differences}
An interesting find is the strength of the SVM algorithm when comparing its predictive performance to its competitors (\autoref{tab:best-learner-perf}).

@@

\subsubsection{Linking feature importance to spectral characteristics}

@@

% RQ4: Which features are most important for the models and how can these be interpreted in an ecological context?
Features along the red-edge wavelength region were most important for models to achieve good predictions.
With respect to dedicated vegetation indices, the "Vogelmann" index with all of its derivatives was seen as the most important index for the best performing SVM model.
This matches well with the actual purpose of these indices: 
These were invented to detect defoliation on sugar marple trees (\textit{Acer saccharum Marsh.}) caused by pear thrips (\textit{Taeniothrips inconsequens Uzel}) in 1988 \cite{vogelmann1993}.

>>>>

@@

\subsubsection{Model differences}
An interesting find is the strength of the SVM algorithm when comparing its predictive performance to its competitors (\autoref{tab:best-learner-perf}).

@@

\subsection{Quality of the data}

\noindent The decision to use a buffer of 2 m for the extraction of an observation's reflectance value was a complex decision.
Due to the reported geometric offset of up to 1 m within the hyperspectral data, the possibility of assigning a value to an observation which would actually refer to a different observation was reasonably high.
By using a buffer of 2 meters (or more), the probability of including information from other trees into the final value increases, blurring the actual value of the tree observation.
However, the difference between single pixel values might often be higher than the difference between a smoothed value composed out of a buffer.
In our view using a buffer of 2 m was a good compromise between including information of too many surrounding trees and not accounting for the geometric offset at all.
Even though no results showing the influence of multiple buffer values on the extraction were provided, we hypothesize that the relationships between features would not change substantially, leading to the almost identical model results.

\subsection{Linking feature importance to spectral characteristics}

@@

% RQ4: Which features are most important for the models and how can these be interpreted in an ecological context?
Features along the red-edge wavelength region were most important for models to achieve good predictions.
With respect to dedicated vegetation indices, the "Vogelmann" index with all of its derivatives was seen as the most important index for the best performing SVM model.
This matches well with the actual purpose of these indices: 
These were invented to detect defoliation on sugar maple trees (\textit{Acer saccharum Marsh.}) caused by pear thrips (\textit{Taeniothrips inconsequens Uzel}) in 1988 \cite{vogelmann1993}.
